### 2022-09-18 include/strumenti.tex
minor fix
fix

  ovvero: \texttt{MAP-INT + LCE + PERM + PHI} e \texttt{MAP-BV + THR-BV +
    LCE + PERM + PHI} 

@@

  \item \textbf{BigRePair} e \textbf{ShapedSlp} per la costruzione e l'suo degli

@@

ordine, mentre l'algoritmo \texttt{mathcDynamic}, studiando la trasformata,

>>>>

  ovvero: \texttt{MAP-INT + LCE + PERM + PHI} e \texttt{MAP-BV + LCE + PERM +
    PHI}  

@@

  \item \textbf{BigRePair} e \textbf{ShapedSlp} per la costruzione e l'uso degli

@@

ordine, mentre l'algoritmo \texttt{matchDynamic}, studiando la trasformata,
